Subsetting plant species list by fruiting species

### 2024-06-11 code/L1/L1_P3_TropicalAndes_plant_fruiting_subset.Rmd
add summary code

>>>>

# Summary
```{r}
cat("Number of occurrence records:", nrow(plant_occ_subset), "\n")
cat("Number of species with occurrence records:", length(unique(plant_occ_subset$Accepted_species)), "\n")
```

```{r}
# the number of records and species per trait database
database_summary <- traits_subset %>%
  group_by(DatabaseSource) %>%
  summarise(
    num_records = n(),
    num_species = n_distinct(Accepted_species)
  )

# Print the result
print(database_summary)
```
